Spin orbit alignment for KELT-7b and HAT-P-56b via Doppler tomography with TRES

### 2016-05-05 referee_reply.txt

We thank the referee again for the careful comments and suggestions. Please find below our replies to each comment. The editions made to the manuscript have also been made bold for ease of change tracking.

>> 1) I appreciate that these changes are minor, and will have had little impact on the functionality of the pipeline. However, I think a single sentence to state that it was optimized or modified to work with TrES data is warranted.

We have noted the minor changes to the pipeline below as follows:

“Details of the spectral reduction and extraction can be found in Buchhave et al. (2010).”
->
“Details of the spectral reduction and extraction is similar to that described in Buchhave et al. (2010) for FIES observations. The pipeline was modified to work with the TRES spectrograph. All the parameters pertaining to the detector and spectrograph were modified, like the CCD format including overscan regions, the gain and readout noise, an initial guess for the position of the ThAr lines. Furthermore, tweaks were made for the handling of 3D cosmic ray removal, 3D profiling to remove pixel-to-pixel variations. However, these modifications are mostly minor changes and the bulk of the pipeline did not need major modifications to work with TRES.”

>> 2) [Regarding the dependence between the assumed template and the measured vsini] I find this last point particularly interesting, and one that might warrant further investigation in the future; for this work, however, I think that is unnecessary. I would like to see a reference to the fact that this was the case in the manuscript though.

To clarify, our previous response: “We found that the derived vsini is significantly dependent on the assumed template, a systematic that we correct for.” referred to the broadening applied to the template, not the Teff, logg, [Fe/H] of the template. That is, the vsini is overestimated when we use a template that does not account for macroturbulence and instrumental broadening.

The following sentence has been appended to the end of paragraph 2, Section 2.3.

"From these tests, we also note that the vsini measurement can be overestimated when we use a template that does not account for macroturbulence and instrumental broadening. "

>> 3) [Regarding testing the assumption of incorrect stellar parameters to the our final result] Again, I find this last point quite valuable, as it demonstrates the robustness of the authors’ MCMC analysis. I think this is valuable information to add to the relevant discussion in the manuscript.

The following paragraph has been added to the end of Section 3 to describe the influence of incorrect stellar parameters on our results.

“To test the effect of a systematic offset in the assumed stellar parameters on our final result, we deconvolved the KELT-7 spectra against a 7000K template,  and modelled this new set of broadening profiles in our global MCMC analysis, whilst imposing a stellar parameter Gaussian prior of Teff=7000K, logg=4.2 for the MCMC jump parameters. We arrive at the same set of planet parameters, with no significant change in the best fit values or uncertainties.”

>> 5) I would like to see the hyper-parameters specified as such, as unless I have missed it in my reading of the manuscript, this is not done.

We have now appended this definition beneath equation 1).

“The Gaussian process hyper-parameters A and tau specify the amplitude and the scale length of the covariance between the velocity points, respectively.”

We have also appended the following footnote to Table 2 to clarify the A and tau variables

^c Gaussian process hyper-parameters A and tau describe the amplitude and the scale length of the covariance between velocity points in the broadening profile modelling.

>> 6) [Regarding MCMC walker parameters listed in Table 2] Again, I would like to see it specified in the table caption that these are the walker parameters. I appreciate the indication as to the use of priors.

We have changed the caption of Table 2 to

“Derived transit geometry parameters”
->
“Derived values for MCMC walker parameters”

>> 7) [Regarding the comparison between our target vsinis and rotation rates of Kepler stars] These are valuable comparisons that I would to see added to the text.

The following sentences have been appended to the end of Paragraph 3, Section 4.1.

“For a consistency check on the assumption that these two systems are also in line-of-sight alignment, we compare the vsini of these stars to that expected from the rotation periods of Kepler stars of similar stellar parameters Nielson et al. (2013). For F-dwarfs like KELT-7 (6600 < Teff < 6800), 68% of stars have rotation periods that lie within 1.2 -- 5.9 days. The vsini-derived rotation period of the KELT-7 is 1.08 days, consistent with the population, and with an aligned geometry. For stars like HAT-P-56 (6400 < Teff < 6600), 68% of stars lie within rotation periods of 1.4 -- 8.6 days. The rotation period of HAT-P-56 from vsini is 1.8 days, again consistent with the distribution, and with alignment.”

>> 8) [ Regarding the potential pulsation signal seen in the Doppler tomographic observation of KELT-7] If this is a real signal then it warrants a mention in the text, particularly if it is not present in the photometry (although I note that none of the photometry is simultaneous with the spectroscopic transit observations). I am not requesting detailed analysis of the signal, but to those practiced at examining Dopplergrams it is obvious, and the lack of any reference to it is equally so. Some reference, and a brief discussion, is thus warranted in my opinion.

We have added the following sentence to Section 4, making note of the pulsation signal.

“We also note a weak stellar pulsation signal is seen in the Doppler tomographic analysis of KELT-7, manifested as diagonal stripes in Figure 3. Pulsations were not detected in the discovery KELT light curves of the star, but their presence is not surprising given the star lies close to the instability strip. Similar pulsations are also seen in the Doppler tomographic observations of WASP-33b (Collier Cameron et al. 2010b, Johnson et al. 2015) and HAT-P-57b (Hartman et al. 2015). “

### 2016-05-05 paper.tex
Revision 2

{\renewcommand{\arraystretch}{1.4} %<- modify value to suit your needs

@@

\date{Submitted XXX}

@@

Spectroscopic observations of the transits were obtained with the Tillinghast Reflector Echelle Spectrograph (TRES) on the 1.5\,m telescope at the Fred Lawrence Whipple Observatory, Mount Hopkins, Arizona, USA. The spectrograph has a resolving power of $\lambda / \Delta \lambda \equiv R = 44000$, sampling the spectral range of 3850-9100\,\AA\, over 51 echelle orders. We use the archival spectroscopic transit data of KELT-7b, originally presented by \citet{2015AJ....150...12B}. The observation was performed on 2013-10-19 UT, a total of 29 spectra were observed, each with 900\,s exposure time made up of three exposures in order to optimize the removal of cosmic rays. The set of spectra achieved an average signal-to-noise per resolution element of $\text{S/N} \sim 160$ over the Mg b line region. Wavelength calibration is achieved by a sequence of Th-Ar hollow cathode lamp exposures that bracket each 900s exposure. The transit of HAT-P-56b was observed on 2016-01-03 UT, with a total of 30 spectra obtained. Similar to the KELT-7b observations, each spectrum was combined from an average of three short exposures, with a total exposure time of 540\,s, achieving an average S/N of $\sim35$. Details of the spectral reduction and extraction can be found in \citet{2010ApJ...720.1118B}.

@@

Each echelle order of the TRES spectrum is first blaze corrected and continuum normalised. We then derive broadening profiles for consecutive sections of the spectrum, each spanning three echelle orders $(\sim 200\,\text{\AA})$. A 20\% trapazium apodisation is applied to the observed spectrum and template to reduce the artefacts that are induced by the deconvolution. The broadening profiles from each section are average combined to form the final rotational profile for each exposure. A total of 34 echelle orders were used, spanning the spectral range 3900--6250\,\AA. This region was chosen to best avoid the telluric absorption lines. We found that deconvolutions of spectra stitched from three consecutive echelle orders yielded lower noise in the final rotational profile than either deconvolution of individual echelle orders, or deconvolution of the entire stitched spectrum. The $\sim 200\,$\AA\, long spectral regions contain enough information to allow an effective deconvolution, and are small enough that the sections can be weighted to arrive at the highest signal-to-noise averaged profile. The radial velocity shift of the star through the transit sequence, determined from the published orbit, is then subtracted, such that the centroid of each rotation kernel is shifted to $0\,\text{km\,s}^{-1}$.

@@

To check if the $v\sin i$ can be accurately recovered from the combination of broadening factors, we generated a series of spectra with $v\sin i=50\,\text{km\,s}^{-1}$, macroturbulence of 0 to $10\,\text{km\,s}^{-1}$, and instrumental broadening of $6\,\text{km\,s}^{-1}$ (as per TRES resolution). These are deconvolved against an unbroadened template to derive broadening profiles for each test synthetic spectrum (Figure~\ref{fig:vmacro}). We fit the broadening kernel with the convolution of a rotation term \citep[modelled analytically from][]{2005oasp.book.....G} and a Gaussian term to account for macroturbulence \citep[expected for F-stars at $6500\,\text{K}$ to be $\sim 6\,\text{km\,s}^{-1}$][]{2014MNRAS.444.3592D} and instrumental broadening. This is different to the SPC approach, which cross correlates a series of spectral templates to the observed spectra, and maximises the cross correlation function peak. Figure~\ref{fig:vmacro} shows the $v\sin i$ can be recovered to within $0.2\,\text{km\,s}^{-1}$.

@@

The per point uncertainties in the rotational profile residuals were estimated by taking the standard deviation of the baseline regions of the rotational profile. We accounted for correlated noise in the broadening kernel via a Gaussian Processes approach \citep[e.g.][]{2015AJ....150..197H}. Applications of Gaussian process regression to astronomical signals have been extensively covered in the literature and shown to reliably retrieve model parameters from data-sets influenced by stochastic noise sources \citep[e.g.][]{2012MNRAS.419.2683G,2014MNRAS.445.3401G}. The Gaussian process regression was modelled with the \emph{George} module \citep{2014arXiv1403.6015A}. We employed a radial exponential kernel to model the co-variance $\Sigma_{ij}$ between points $i$, $j$, with velocities $v_{i}$ and $v_{j}$:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{|v_{i}-v_{j}|}{\tau} \right)\,,
\end{equation}
where $\sigma_{i}$ is the per-point uncertainty for point $i$, and $\delta_{ij}$ is the Kronecker delta function.

We explored the parameter space with a Markov chain Monte Carlo (MCMC) analysis, using the \emph{emcee} implementation \citep{2013PASP..125..306F} of an affine-invariant ensemble sampler. The transit parameters are also constrained by the spectroscopic stellar parameters for each star. At each iteration, we calculate an expected $a/R_\star$ using the orbital period, stellar mass and radii expected for the spectroscopic $T_\text{eff}$, $\log g$, [Fe/H] of the spectrum. The stellar mass and radius are interpolated from the spectroscopic parameters via the \citet{2010A&amp;ARv..18...67T} relationships. The expected $a/R_\star$ is then compared to the tested $a/R_\star$, thereby constraining the fit. The spectroscopic $v \sin i$ measurement and uncertaintiy from Section~\ref{sec:lsd} is applied to the fit as Gaussian prior. Gaussian priors were also imposed on the transit centre $T_0$ and period $P$, since these were derived in the discovery papers from the discovery and follow-up light curves, and are therefore much better constrained than from follow-up light curves alone. Uniform priors were assumed for all other parameters, including the hyper-parameters of the Gaussian process regression.

@@

  \caption{\label{tab:parameters}Derived transit geometry parameters}
  \begin{tabular}{lrr}
    \hline\hline
    & \textbf{KELT-7b} & \textbf{HAT-P-56b}\\
    \hline
    Period (days) $^a$ & $2.734780_{-0.000003}^{+0.000003}$& $2.790833_{-0.000004}^{+0.000004}$ \\
    $T_0$ (BJD)  $^a$  & $2456355.2293_{-0.0001}^{+0.0001}$ & $2456553.6164_{-0.0003}^{+0.0003}$ \\
    $R_p/R_\star$  & $0.0922_{-0.0004}^{+0.0004}$ & $0.099_{-0.002}^{+0.002}$ \\
    $a/R_\star$  & $5.50_{-0.06}^{+0.06}$ &  $6.7_{-0.4}^{+0.5}$ \\
    $\text{inc}\,(^\circ)$  & $83.7_{-0.2}^{+0.2}$ & $82.6_{-0.6}^{+0.7}$\\
    $|\lambda|\,(^\circ)$  & $2.7_{-0.6}^{+0.6}$ & $7_{-2}^{+2}$\\
    $v\sin i\,(\text{km\,s}^{-1})$  $^b$  & $69.3_{-0.2}^{+0.2}$ & $36.4_{-0.7}^{+0.7}$\\
    $\ln(A)$  & $-9.17_{-0.04}^{+0.05}$ & $-7.65_{-0.05}^{+0.05}$ \\
    $\ln(\tau)$  & $3.6_{-0.1}^{+0.1}$ & $2.24_{-0.1}^{+0.1}$\\
    $T_\mathrm{eff}$ (K) $^a$  & $6513_{-53}^{+49}$& $6568_{-53}^{+51}$\\
    $\log g$  & $4.14_{-0.03}^{+0.03}$ $^a$ & $4.26_{-0.05}^{+0.06}$\\
    \hline
  \end{tabular}
  \begin{flushleft}
  $^a$ Gaussian priors according to literature values were imposed.\\
  $^b$ Gaussian priors according to $v\sin i$ estimates from Section~\ref{sec:vsini} were imposed.  
  \end{flushleft}
\end{table*}

@@

@@

The transit parameters we derived for KELT-7b and HAT-P-56b are in general agreement with those in the discovery papers. KELT-7b is confirmed to be in a spin-orbit aligned geometry, in agreement with the Rossiter-McLaughlin analysis in \citet{2015AJ....150...12B}. In fact, \citet{2015AJ....150...12B} were able to detect the shadow of the planet in the cross correlation function of the spectra. Because of the grazing nature of the transit of HAT-P-56b, the uncertainties in its transit parameters are larger than the other systems. The uncertainities we derive for HAT-P-56b are are larger than those in the discovery paper, we find $R_p/R_\star = 0.099_{-0.002}^{+0.002}$ and $a/R_\star = 6.7_{-0.4}^{+0.5}$, compared to $R_p/R_\star = 0.1054\pm0.0009$ and $a/R_\star = 6.37\pm0.11$ from the discovery paper. The uncertainty in the planet radius is unchanged, since it is dominated by the uncertainty in the stellar radius, rather than in $R_p/R_\star$.

@@

Have these systems undergone tidal synchronisation and realignment? The characteristic timescale for stellar spin sychronisation is given by \citet{2010ApJ...723..285H} and \citet{2012ApJ...757....6H}, who reviewed the tidal theory in the context of hot-Jupiter systems. Adopting Equation 3 in \citet{2012ApJ...757....6H}, the characteristic timescale to modify the spin of the host star, $T_\text{spin}$, is:
\begin{align}
  T_\text{spin} =& \frac{3.1\times10^9\,\text{years}}{(1-e^2)^{1/2}} \left(\frac{a}{0.02 \,\text{AU}} \right)^{7.5} \left( \frac{R_\star}{R_\odot}\right)^{-8} \left( \frac{k_0^2}{0.1} \right) \notag\\
  &\times \left( \frac{30 \,\text{days}}{P_\text{rot}} \right) \left(\frac{M_\star + M_p}{M_\odot} \right)^{1/2} \left(\frac{M_p}{M_\text{Jup}} \right)^{-2} \notag\\
  &\times \left( \frac{\sigma_\star}{7.8\times10^{-8}} \right)^{-1}\,.
\end{align}
We assume a stellar gyration radius of $k_0^2=0.1\,R_\star ^2$ \citep{2000MNRAS.315..543H}, stellar dissipation coefficients $\sigma_\star$ of $10^{-12}$ for KELT-7, and $10^{-8}$ for  HAT-P-56 \citep[from Figure 3 of][]{2012ApJ...757....6H}. The expected $T_\text{spin}$ is $\sim 10^{16}$ years for KELT-7 and $10^{12}$ years for HAT-P-56b. That is, tidal dissipation in the stellar envelope is expected to be weak for KELT-7 and HAT-P-56, at least based on standard equilibrium tide models. In fact, tidal interactions are expected to be weak for all the spin-orbit aligned hot-Jupiters around F-dwarfs. Only the transiting brown dwarf KELT-1b \citep{2012ApJ...761..123S}, found around a rapidly rotating F-star in a 1.2\,d period orbit, has a short tidal realignment timescale ($10^8$ years).

KELT-7b and HAT-P-56b were found to be in projected spin-orbit alignment. If we assume alignment in the line-of-sight of the stellar spin axis as well, we can examine the spin-orbit coupling of these systems. The spins of KELT-7 and HAT-P-56 are both super-synchronous with respect to the orbital period of the planet. The maximum rotation period for KELT-7 is $1.08\pm0.03$ days, and $1.8\pm0.2$ days for HAT-P-56, based on the spectroscopic $v \sin i$ measurements. From the K2 light curves, \citet{2015AJ....150...85H} found that HAT-P-56 is a possible $\gamma$ Dor pulsator with a primary pulsation period of $1.64\pm0.03$ days, and a secondary peak in the periodogram of $1.74\pm0.02$ days that is consistent with the $v\sin i$ derived rotation period. Neither the KELT discovery light curves, nor the archival SuperWASP light curves \citep{2010A&amp;A...520L..10B} yielded a photometric modulation period for KELT-7 in our analysis.  For comparison, \citet{2013MNRAS.436.1883W} found that \emph{Kepler} systems with planets of $R_p > 6 \,R_\text{E}$ and $\text{Period}<10$\,days are preferentially found in the stellar-spin -- planet-orbit synchronised states. The four that were systems found to be in super-synchronous states had orbital periods greater than 5 days, the largest of which had a radius of $0.7\,R_\mathrm{J}$.

@@

Given the lack of evidence for tidal evolution in the rotation periods of most hot host stars, we can examine the set of spin-orbit angles for these systems around hot stars in the context of migration mechanisms. 23\% of the systems around hot stars are found in spin-orbit aligned arrangements. While the fraction of aligned systems is significantly lower than that of the overall distribution, it is still different from the relatively even $\lambda$ distribution expected from dynamical interactions such as eccentric migration via stellar binary Kozai-Lidov cycles \citep[e.g.][]{2012ApJ...754L..36N,2015ApJ...799...27P} or planet-planet scattering \citep[e.g.][]{2011ApJ...742...72N}. Nevertheless, dynamical interactions, compared to in-disk co-planar migration, are likely responsible for a significant fraction of hot-Jupiters around hot stars. It should be noted that inhomogenieity of the star-forming cloud, or binary-induced disk tilting, will also cause primordial spin-orbit misalignment \citep{2010MNRAS.401.1505B,2012Natur.491..418B}. We also note \citet{2012ApJ...758L...6R} suggest that internal gravity waves at the convective core -- radiative envelope boundary can induce arbitary surface spins for hot stars, independent of star-planet interactions.

>>>>

%{\renewcommand{\arraystretch}{1.4} %<- modify value to suit your needs

@@

\date{Submitted 2016-04-27}

@@

Spectroscopic observations of the transits were obtained with the Tillinghast Reflector Echelle Spectrograph (TRES) on the 1.5\,m telescope at the Fred Lawrence Whipple Observatory, Mount Hopkins, Arizona, USA. The spectrograph has a resolving power of $\lambda / \Delta \lambda \equiv R = 44000$, sampling the spectral range of 3850-9100\,\AA\, over 51 echelle orders. We use the archival spectroscopic transit data of KELT-7b, originally presented by \citet{2015AJ....150...12B}. The observation was performed on 2013-10-19 UT, a total of 29 spectra were observed, each with 900\,s exposure time made up of three exposures in order to optimize the removal of cosmic rays. The set of spectra achieved an average signal-to-noise per resolution element of $\text{S/N} \sim 160$ over the Mg b line region. Wavelength calibration is achieved by a sequence of Th-Ar hollow cathode lamp exposures that bracket each 900s exposure. The transit of HAT-P-56b was observed on 2016-01-03 UT, with a total of 30 spectra obtained. Similar to the KELT-7b observations, each spectrum was combined from an average of three short exposures, with a total exposure time of 540\,s, achieving an average S/N of $\sim35$. \textbf{Details of the spectral reduction and extraction is similar to that described in \citet{2010ApJ...720.1118B} for FIES observations. The pipeline was modified to work with the TRES spectrograph. All the parameters pertaining to the detector and spectrograph were modified, like the CCD format including overscan regions, the gain and readout noise, an initial guess for the position of the ThAr lines. Furthermore, tweaks were made for the handling of 3D cosmic ray removal, 3D profiling to remove pixel-to-pixel variations. However, these modifications are mostly minor changes and the bulk of the pipeline did not need major modifications to work with TRES.}

@@

Each echelle order of the TRES spectrum is first blaze corrected and continuum normalised. We then derive broadening profiles for consecutive sections of the spectrum, each spanning three echelle orders $(\sim 200\,\text{\AA})$. A 20\% trapezium apodisation is applied to the observed spectrum and template to reduce the artifacts that are induced by the deconvolution. The broadening profiles from each section are average combined to form the final rotational profile for each exposure. A total of 34 echelle orders were used, spanning the spectral range 3900--6250\,\AA. This region was chosen to best avoid the telluric absorption lines. We found that deconvolutions of spectra stitched from three consecutive echelle orders yielded lower noise in the final rotational profile than either deconvolution of individual echelle orders, or deconvolution of the entire stitched spectrum. The $\sim 200\,$\AA\, long spectral regions contain enough information to allow an effective deconvolution, and are small enough that the sections can be weighted to arrive at the highest signal-to-noise averaged profile. The radial velocity shift of the star through the transit sequence, determined from the published orbit, is then subtracted, such that the centroid of each rotation kernel is shifted to $0\,\text{km\,s}^{-1}$.

@@

To check if the $v\sin i$ can be accurately recovered from the combination of broadening factors, we generated a series of spectra with $v\sin i=50\,\text{km\,s}^{-1}$, macroturbulence of 0 to $10\,\text{km\,s}^{-1}$, and instrumental broadening of $6\,\text{km\,s}^{-1}$ (as per TRES resolution). These are deconvolved against an unbroadened template to derive broadening profiles for each test synthetic spectrum (Figure~\ref{fig:vmacro}). We fit the broadening kernel with the convolution of a rotation term \citep[modelled analytically from][]{2005oasp.book.....G} and a Gaussian term to account for macroturbulence \citep[expected for F-stars at $6500\,\text{K}$ to be $\sim 6\,\text{km\,s}^{-1}$][]{2014MNRAS.444.3592D} and instrumental broadening. This is different to the SPC approach, which cross correlates a series of spectral templates to the observed spectra, and maximises the cross correlation function peak. Figure~\ref{fig:vmacro} shows the $v\sin i$ can be recovered to within $0.2\,\text{km\,s}^{-1}$. \textbf{From these tests, we also note that the $v\sin i$ measurement can be overestimated when we use a template that does not account for macroturbulence and instrumental broadening. }

@@

The per point uncertainties in the rotational profile residuals were estimated by taking the standard deviation of the baseline regions of the rotational profile. We accounted for correlated noise in the broadening kernel via a Gaussian Processes approach \citep[e.g.][]{2015AJ....150..197H}. Applications of Gaussian process regression to astronomical signals have been extensively covered in the literature and shown to reliably retrieve model parameters from data-sets influenced by stochastic noise sources \citep[e.g.][]{2012MNRAS.419.2683G,2014MNRAS.445.3401G}. The Gaussian process regression was modelled with the \emph{George} module \citep{2014arXiv1403.6015A}. We employed a radial exponential kernel to model the co-variance $\Sigma_{ij}$ between points $i$, $j$, with velocities $v_{i}$ and $v_{j}$:
\begin{equation}
  \Sigma_{ij} = \sigma_{i}^2 \delta_{ij} + A \exp \left(- \frac{|v_{i}-v_{j}|}{\tau} \right)\,,
\end{equation}
where $\sigma_{i}$ is the per-point uncertainty for point $i$, and $\delta_{ij}$ is the Kronecker delta function. \textbf{The Gaussian process hyper-parameters $A$ and $\tau$ specify the amplitude and the scale length of the covariance between the velocity points, respectively.}

We explored the parameter space with a Markov chain Monte Carlo (MCMC) analysis, using the \emph{emcee} implementation \citep{2013PASP..125..306F} of an affine-invariant ensemble sampler. The transit parameters are also constrained by the spectroscopic stellar parameters for each star. At each iteration, we calculate an expected $a/R_\star$ using the orbital period, stellar mass and radii expected for the spectroscopic $T_\text{eff}$, $\log g$, [Fe/H] of the spectrum. The stellar mass and radius are interpolated from the spectroscopic parameters via the \citet{2010A&amp;ARv..18...67T} relationships. The expected $a/R_\star$ is then compared to the tested $a/R_\star$, thereby constraining the fit. The spectroscopic $v \sin i$ measurement and uncertainty from Section~\ref{sec:lsd} is applied to the fit as Gaussian prior. Gaussian priors were also imposed on the transit centre $T_0$ and period $P$, since these were derived in the discovery papers from the discovery and follow-up light curves, and are therefore much better constrained than from follow-up light curves alone. Uniform priors were assumed for all other parameters, including the hyper-parameters of the Gaussian process regression.

@@

  \caption{\label{tab:parameters}Derived values for MCMC walker parameters}
  \begin{tabular}{lrr}
    \hline\hline
    & \textbf{KELT-7b} & \textbf{HAT-P-56b}\\
    \hline
    Period (days) $^a$ & $2.734780_{-0.000003}^{+0.000003}$& $2.790833_{-0.000004}^{+0.000004}$ \\
    $T_0$ (BJD)  $^a$  & $2456355.2293_{-0.0001}^{+0.0001}$ & $2456553.6164_{-0.0003}^{+0.0003}$ \\
    $R_p/R_\star$  & $0.0922_{-0.0004}^{+0.0004}$ & $0.099_{-0.002}^{+0.002}$ \\
    $a/R_\star$  & $5.50_{-0.06}^{+0.06}$ &  $6.7_{-0.4}^{+0.5}$ \\
    $\text{inc}\,(^\circ)$  & $83.7_{-0.2}^{+0.2}$ & $82.6_{-0.6}^{+0.7}$\\
    $|\lambda|\,(^\circ)$  & $2.7_{-0.6}^{+0.6}$ & $7_{-2}^{+2}$\\
    $v\sin i\,(\text{km\,s}^{-1})$  $^b$  & $69.3_{-0.2}^{+0.2}$ & $36.4_{-0.7}^{+0.7}$\\
    $\ln(A)$ $^c$  & $-9.17_{-0.04}^{+0.05}$ & $-7.65_{-0.05}^{+0.05}$ \\
    $\ln(\tau)$ $^c$ & $3.6_{-0.1}^{+0.1}$ & $2.24_{-0.1}^{+0.1}$\\
    $T_\mathrm{eff}$ (K) $^a$  & $6513_{-53}^{+49}$& $6568_{-53}^{+51}$\\
    $\log g$  & $4.14_{-0.03}^{+0.03}$ $^a$ & $4.26_{-0.05}^{+0.06}$\\
    \hline
  \end{tabular}
  \begin{flushleft}
  $^a$ Gaussian priors according to literature values were imposed.\\
  $^b$ Gaussian priors according to $v\sin i$ estimates from Section~\ref{sec:vsini} were imposed.  \\
  $^c$ \textbf{Gaussian process hyper-parameters $A$ and $\tau$ describe the amplitude and the scale length of the covariance between velocity points in the broadening profile modelling.}
  \end{flushleft}
\end{table*}

@@

\textbf{To test the effect of a systematic offset in the assumed stellar parameters on our final result, we deconvolved the KELT-7 spectra against a 7000\,K template,  and modelled this new set of broadening profiles in our global MCMC analysis, whilst imposing a stellar parameter Gaussian prior of $T_\mathrm{eff}=7000$\,K, $\log g=4.2$ for the MCMC jump parameters. We arrive at the same set of planet parameters, with no significant change in the best fit values or uncertainties.}

@@

The transit parameters we derived for KELT-7b and HAT-P-56b are in general agreement with those in the discovery papers. KELT-7b is confirmed to be in a spin-orbit aligned geometry, in agreement with the Rossiter-McLaughlin analysis in \citet{2015AJ....150...12B}. In fact, \citet{2015AJ....150...12B} were able to detect the shadow of the planet in the cross correlation function of the spectra. Because of the grazing nature of the transit of HAT-P-56b, the uncertainties in its transit parameters are larger than the other systems. The uncertainties we derive for HAT-P-56b are are larger than those in the discovery paper, we find $R_p/R_\star = 0.099_{-0.002}^{+0.002}$ and $a/R_\star = 6.7_{-0.4}^{+0.5}$, compared to $R_p/R_\star = 0.1054\pm0.0009$ and $a/R_\star = 6.37\pm0.11$ from the discovery paper. The uncertainty in the planet radius is unchanged, since it is dominated by the uncertainty in the stellar radius, rather than in $R_p/R_\star$. \textbf{We also note a weak stellar pulsation signal is seen in the Doppler tomographic analysis of KELT-7, manifested as diagonal stripes in Figure~\ref{fig:dopplergram}). Pulsations were not detected in the discovery KELT light curves of the star, but their presence not surprising given the star lies close to the instability strip. Similar pulsations are also seen in the Doppler tomographic observations of WASP-33b \citep{2010MNRAS.407..507C,2015ApJ...810L..23J} and HAT-P-57b \citep{2015AJ....150..197H}. }

@@

Have these systems undergone tidal synchronisation and realignment? The characteristic timescale for stellar spin synchronisation is given by \citet{2010ApJ...723..285H} and \citet{2012ApJ...757....6H}, who reviewed the tidal theory in the context of hot-Jupiter systems. Adopting Equation 3 in \citet{2012ApJ...757....6H}, the characteristic timescale to modify the spin of the host star, $T_\text{spin}$, is:
\begin{align}
  T_\text{spin} =& \frac{3.1\times10^9\,\text{years}}{(1-e^2)^{1/2}} \left(\frac{a}{0.02 \,\text{AU}} \right)^{7.5} \left( \frac{R_\star}{R_\odot}\right)^{-8} \left( \frac{k_0^2}{0.1} \right) \notag\\
  &\times \left( \frac{30 \,\text{days}}{P_\text{rot}} \right) \left(\frac{M_\star + M_p}{M_\odot} \right)^{1/2} \left(\frac{M_p}{M_\text{Jup}} \right)^{-2} \notag\\
  &\times \left( \frac{\sigma_\star}{7.8\times10^{-8}} \right)^{-1}\,.
\end{align}
We assume a stellar gyration radius of $k_0^2=0.1\,R_\star ^2$ \citep{2000MNRAS.315..543H}, stellar dissipation coefficients $\sigma_\star$ of $10^{-12}$ for KELT-7, and $10^{-8}$ for  HAT-P-56 \citep[from Figure 3 of][]{2012ApJ...757....6H}. The expected $T_\text{spin}$ is $\sim 10^{16}$ years for KELT-7 and $10^{12}$ years for HAT-P-56b. That is, tidal dissipation in the stellar envelope is expected to be weak for KELT-7 and HAT-P-56, at least based on standard equilibrium tide models. In fact, tidal interactions are expected to be weak for all the spin-orbit aligned hot-Jupiters around F-dwarfs. Only the transiting brown dwarf KELT-1b \citep{2012ApJ...761..123S}, found around a rapidly rotating F-star in a 1.2\,d period orbit, has a short tidal realignment timescale ($10^8$ years).

KELT-7b and HAT-P-56b were found to be in projected spin-orbit alignment. If we assume alignment in the line-of-sight of the stellar spin axis as well, we can examine the spin-orbit coupling of these systems. The spins of KELT-7 and HAT-P-56 are both super-synchronous with respect to the orbital period of the planet. The maximum rotation period for KELT-7 is $1.08\pm0.03$ days, and $1.8\pm0.2$ days for HAT-P-56, based on the spectroscopic $v \sin i$ measurements. From the K2 light curves, \citet{2015AJ....150...85H} found that HAT-P-56 is a possible $\gamma$ Dor-pulsator with a primary pulsation period of $1.64\pm0.03$ days, and a secondary peak in the periodogram of $1.74\pm0.02$ days that is consistent with the $v\sin i$ derived rotation period. Neither the KELT discovery light curves, nor the archival SuperWASP light curves \citep{2010A&amp;A...520L..10B} yielded a photometric modulation period for KELT-7 in our analysis.  For comparison, \citet{2013MNRAS.436.1883W} found that \emph{Kepler} systems with planets of $R_p > 6 \,R_\text{E}$ and $\text{Period}<10$\,days are preferentially found in the stellar-spin -- planet-orbit synchronised states. The four that were systems found to be in super-synchronous states had orbital periods greater than 5 days, the largest of which had a radius of $0.7\,R_\mathrm{J}$. \textbf{For a consistency check on the assumption that these two systems are also in line-of-sight alignment, we can compare the $v\sin i$ of these stars to that expected from the rotation periods of Kepler stars of similar stellar parameters \citep{2013A&amp;A...557L..10N}. For F-dwarfs like KELT-7 ($6600 < T_\mathrm{eff} < 6800$), 68\% of stars have rotation periods that lie within 1.2 -- 5.9 days. The $v\sin i$-derived rotation period of the KELT-7 is 1.08 days, consistent with the population, and with an aligned geometry. For stars like HAT-P-56 ($6400 < T_\mathrm{eff} < 6600$), 68\% of stars lie within rotation periods of 1.4 -- 8.6 days. The rotation period of HAT-P-56 from $v\sin i$ is 1.8 days, again consistent with the distribution, and with alignment.}

@@

Given the lack of evidence for tidal evolution in the rotation periods of most hot host stars, we can examine the set of spin-orbit angles for these systems around hot stars in the context of migration mechanisms. 23\% of the systems around hot stars are found in spin-orbit aligned arrangements. While the fraction of aligned systems is significantly lower than that of the overall distribution, it is still different from the relatively even $\lambda$ distribution expected from dynamical interactions such as eccentric migration via stellar binary Kozai-Lidov cycles \citep[e.g.][]{2012ApJ...754L..36N,2015ApJ...799...27P} or planet-planet scattering \citep[e.g.][]{2011ApJ...742...72N}. Nevertheless, dynamical interactions, compared to in-disk co-planar migration, are likely responsible for a significant fraction of hot-Jupiters around hot stars. It should be noted that inhomogeneity of the star-forming cloud, or binary-induced disk tilting, will also cause primordial spin-orbit misalignment \citep{2010MNRAS.401.1505B,2012Natur.491..418B}. We also note \citet{2012ApJ...758L...6R} suggest that internal gravity waves at the convective core -- radiative envelope boundary can induce arbitrary surface spins for hot stars, independent of star-planet interactions.
